Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-08-07 manuscript/appendix.Rmd
fixed appendix citations
merged appendix_library into library.bib, deleted
knit appendix

bibliography: appendix_library.bib
csl: global-change-biology.csl
nocite: | 
  @hijmans_very_2005; @fick_worldclim_2017; @harris_updated_2014;  @abatzoglou_terraclimate_2018; @trabucco_global_2019

>>>>

bibliography: library.bib
csl: global-change-biology.csl
nocite: | 
  @hijmans_very_2005; @fick_worldclim_2017; @harris_updated_2014;  @abatzoglou_terraclimate_2018; @trabucco_global_2019
